### 2020-11-24 presentation/intro.tex
add presentation template

\section{Introduction}

\begin{frame}{Slide One}

\end{frame}

\begin{frame}{Slide Two}

\end{frame}

\begin{frame}{Slide Three}

\end{frame}

### 2020-11-26 code/scripts/sbox-table.js
Add a readable sbox table and the generating script

@@ -1,0 +1,23 @@
+const { sbox } = require('./sbox');
+const nums = Array(16)
+	.fill(0)
+	.map((_, i) => i.toString(16));
+
+console.log(`\\begin{tabular}{|r||${'r|'.repeat(16)}}
+\\hline`);
+
+console.log(`  & ${nums.map(v => v.padStart(2, '0')).join(' & ')} \\\\
+\\hline  \\hline`);
+
+for (let i = 0; i < 16; i++) {
+	let row = `${nums[i].padEnd(2, '0')}`;
+
+	for (let j = 0; j < 16; j++) {
+		const out = sbox[i * 16 + j];
+		row += ` & ${out.toString(16).padEnd(2, '0')}`;
+	}
+	console.log(`${row} \\\\
+\\hline`);
+}
+
+console.log(`\\end{tabular}`);

### 2020-11-26 code/scripts/sbox.js

@@ -1,0 +1,258 @@
+exports.sbox = [
+	177,
+	206,
+	195,
+	149,
+	90,
+	173,
+	231,
+	2,
+	77,
+	68,
+	251,
+	145,
+	12,
+	135,
+	161,
+	80,
+	203,
+	103,
+	84,
+	221,
+	70,
+	143,
+	225,
+	78,
+	240,
+	253,
+	252,
+	235,
+	249,
+	196,
+	26,
+	110,
+	94,
+	245,
+	204,
+	141,
+	28,
+	86,
+	67,
+	254,
+	7,
+	97,
+	248,
+	117,
+	89,
+	255,
+	3,
+	34,
+	138,
+	209,
+	19,
+	238,
+	136,
+	0,
+	14,
+	52,
+	21,
+	128,
+	148,
+	227,
+	237,
+	181,
+	83,
+	35,
+	75,
+	71,
+	23,
+	167,
+	144,
+	53,
+	171,
+	216,
+	184,
+	223,
+	79,
+	87,
+	154,
+	146,
+	219,
+	27,
+	60,
+	200,
+	153,
+	4,
+	142,
+	224,
+	215,
+	125,
+	133,
+	187,
+	64,
+	44,
+	58,
+	69,
+	241,
+	66,
+	101,
+	32,
+	65,
+	24,
+	114,
+	37,
+	147,
+	112,
+	54,
+	5,
+	242,
+	11,
+	163,
+	121,
+	236,
+	8,
+	39,
+	49,
+	50,
+	182,
+	124,
+	176,
+	10,
+	115,
+	91,
+	123,
+	183,
+	129,
+	210,
+	13,
+	106,
+	38,
+	158,
+	88,
+	156,
+	131,
+	116,
+	179,
+	172,
+	48,
+	122,
+	105,
+	119,
+	15,
+	174,
+	33,
+	222,
+	208,
+	46,
+	151,
+	16,
+	164,
+	152,
+	168,
+	212,
+	104,
+	45,
+	98,
+	41,
+	109,
+	22,
+	73,
+	118,
+	199,
+	232,
+	193,
+	150,
+	55,
+	229,
+	202,
+	244,
+	233,
+	99,
+	18,
+	194,
+	166,
+	20,
+	188,
+	211,
+	40,
+	175,
+	47,
+	230,
+	36,
+	82,
+	198,
+	160,
+	9,
+	189,
+	140,
+	207,
+	93,
+	17,
[…]

### 2020-11-26 code/scripts/sbox-analysis.js
Add ddt properties

@@ -1,0 +1,82 @@
+const { sbox } = require('./sbox');
+const size = sbox.length;
+
+// create 2d array filled with zeroes
+const ddt = Array(size)
+	.fill(null)
+	.map(() => Array(size).fill(0));
+
+for (let i = 0; i < size; i++) {
+	// iterate over input difference
+	for (let u0 = 0; u0 < size; u0++) {
+		// iterate over first input
+		let u1 = u0 ^ i, // calculate first input
+			v0 = sbox[u0], // calculate sbox outputs
+			v1 = sbox[u1];
+
+		ddt[i][v0 ^ v1]++; // increment frequency in DDT for v0 xor v1
+	}
+}
+
+/**
+ *
+ * @param {number[][]} ddt
+ */
+const countZeroes = ddt =>
+	ddt
+		.map(row => row.reduce((a, v) => a + Number(v === 0), 0))
+		.reduce((a, v) => a + v, 0);
+
+/**
+ * Number of times x occurs for input difference diff in ddt
+ * @param {number[][]} ddt
+ * @param {number} diff
+ * @param {number} x
+ */
+const countPerInputDiff = (ddt, diff, x) =>
+	ddt[diff].reduce((a, v) => a + Number(v === x), 0);
+
+/**
+ * Number of times x occurs for output difference diff in ddt
+ * @param {number[][]} ddt
+ * @param {number} diff
+ * @param {number} x
+ */
+const countPerOutputDiff = (ddt, diff, x) =>
+	ddt.map(row => row[diff]).reduce((a, v) => a + Number(v === x), 0);
+
+const max = ddt
+	.slice(1)
+	.map(row => row.slice(1))
+	.map(row => row.reduce((p, a) => Math.max(p, a), 0))
+	.reduce((p, a) => Math.max(p, a), 0);
+
+console.log(`Max value in DDT is ${max}`);
+
+for (let i = 0; i < size; i++) {
+	console.log(
+		`Number of 4s for input diff ${i.toString(16)}: `,
+		countPerInputDiff(ddt, i, 4),
+	);
+}
+for (let i = 0; i < size; i++) {
+	console.log(
+		`Number of 2s for input diff ${i.toString(16)}: `,
+		countPerInputDiff(ddt, i, 2),
+	);
+}
+
+for (let i = 0; i < size; i++) {
+	console.log(
+		`Number of 4s for output diff ${i.toString(16)}: `,
[…]

### 2020-11-27 code/square_attack.cpp
Add SQUARE and attack code

@@ -1,0 +1,431 @@
+#include<vector>
+#include<iostream>
+#include<bits/stdc++.h>
+#include<cstdlib>
+
+#define rounds 4
+#define ROOT 0x1f5U /* Generator of GF(2^8), maintains GF(2^8) */
+
+using namespace std;
+
+// Word lengths:
+// sizeof(char) = 8 bits
+// sizeof(short) = 16 bits
+// sizeof(int) = 32 bits
+// sizeof(long) = 64 bits
+
+typedef unsigned char bit8;     // 8 bit word
+typedef unsigned short bit16;   // 16 bit word
+typedef unsigned int bit32;     // 32 bit word
+
+// sbox for block cipher square
+vector<bit16> sbox =
+{0xb1, 0xce ,0xc3 ,0x95 ,0x5a ,0xad ,0xe7 ,0x02 ,0x4d ,0x44 ,0xfb ,0x91 ,0x0c ,0x87 ,0xa1 ,0x50,
+ 0xcb, 0x67 ,0x54 ,0xdd ,0x46 ,0x8f ,0xe1 ,0x4e ,0xf0 ,0xfd ,0xfc ,0xeb ,0xf9 ,0xc4 ,0x1a ,0x6e,
+ 0x5e, 0xf5 ,0xcc ,0x8d ,0x1c ,0x56 ,0x43 ,0xfe ,0x07 ,0x61 ,0xf8 ,0x75 ,0x59 ,0xff ,0x03 ,0x22,
+ 0x8a, 0xd1 ,0x13 ,0xee ,0x88 ,0x00 ,0x0e ,0x34 ,0x15 ,0x80 ,0x94 ,0xe3 ,0xed ,0xb5 ,0x53 ,0x23,
+ 0x4b, 0x47 ,0x17 ,0xa7 ,0x90 ,0x35 ,0xab ,0xd8 ,0xb8 ,0xdf ,0x4f ,0x57 ,0x9a ,0x92 ,0xdb ,0x1b,
+ 0x3c, 0xc8 ,0x99 ,0x04 ,0x8e ,0xe0 ,0xd7 ,0x7d ,0x85 ,0xbb ,0x40 ,0x2c ,0x3a ,0x45 ,0xf1 ,0x42,
[…]

### 2020-11-27 code/square_attack.cpp
Fix Attack code

@@ -411,6 +411,7 @@ void visualise_and_attack(bit16 *key)
          }
       }
    }
+   cout << "\n############### Key found after attack ###############\n";
    for(i = 0; i < 4; i++)
    {
       for(j = 0; j < 4; j++)

### 2020-11-27 presentation/bpnominate.tex
Add presentation (observation, brownie and conclusion)

\section{Brownie Point Nominations}

\begin{frame}{\#1 Figure showing 4 round distinguisher}
  \begin{figure}
    \centering
    \includegraphics[width=\linewidth]{sq_attack1}
    \caption{Integral attack distinguisher}
  \end{figure}
\end{frame}

\begin{frame}{\#2 Integral Attack Implementation}
  C++ Implementation of 4 round integral attack
\end{frame}

\begin{frame}{\#3 Similarity of Inverse Cipher}
  The SQUARE cipher and it's inverse are very similar. We can use the cipher in place of it's inverse just by replacing $\gamma$ with $\gamma^{-1}$, $\theta$ with $\theta^{-1}$ and keys $k^t$ with $\theta(k^{8-t})$.
\end{frame}

### 2020-11-27 presentation/conclu.tex
Add presentation (observation, brownie and conclusion)

\section{Conclusion}

\begin{frame}{Conclusion}
  \begin{beamerboxesrounded}{Similarity with AES}
    SQUARE, which is a predecessor of AES is very similar to AES in it's structure and S-box. And shares some common attacks.
  \end{beamerboxesrounded}
  \vspace{5mm}
  \begin{beamerboxesrounded}{Attacks}
    Practical attacks for up to six rounds are known for SQUARE  and hence the number rounds is 8 following a conservative approach.
  \end{beamerboxesrounded}
  \vspace{5mm}
  \begin{beamerboxesrounded}{Use in real world}
    Even though the known full round attacks are not practical, the authors recommend against using it in applications due to lack of intense public scrutiny.
  \end{beamerboxesrounded}
\end{frame}

### 2020-11-27 presentation/observe.tex
Add presentation (observation, brownie and conclusion)

\section{Observations}

\begin{frame}{DDT}

  \begin{beamerboxesrounded}{DDT Properties}
    \begin{itemize}
      \item Highest value: 4 (Probability $\frac{4}{256}$)
      \item Only contains the values 0, 2 and 4
      \item For any fixed input/output difference
            \begin{itemize}
              \item 4 occurs exactly once
              \item 2 occurs 126 times
              \item 0 occurs 129 times
            \end{itemize}
      \item No of zeroes is 33,150. $\sim$ 50\% difference pairs are impossible.
    \end{itemize}
  \end{beamerboxesrounded}

  Very similar to AES Sbox

\end{frame}

\begin{frame}{Integral Attack}
  \begin{flalign*}
    P_0 &= (0, c_1, c_2 \dotsc c_{15})\\
    P_1 &= (1, c_1, c_2 \dotsc c_{15})\\
    P_2 &= (2, c_1, c_2 \dotsc c_{15})\\
    &\vdots\\
    P_{255} &= (255, c_1, c_2 \dotsc c_{15})
  \end{flalign*}

  \begin{equation*}
    \Lambda = \{P_0, P_1, P_2 \dotsc P_{255}\}
  \end{equation*}
\end{frame}

\begin{frame}{Integral Attack}{Properties}
  \begin{beamerboxesrounded}{All $\mathcal{A}$}
    The byte in which all values appear exactly once among all the
    texts in the set is called the \textbf{all} property.
  \end{beamerboxesrounded}

  \vspace{5mm}

  \begin{beamerboxesrounded}{Constant $\mathcal{C}$}
    The byte in which all texts in the set have an identical value is called the \textbf{constant} property.
  \end{beamerboxesrounded}

  \vspace{5mm}

  \begin{beamerboxesrounded}{Balanced $\mathcal{B}$}
    The byte in which XOR sum of all values is zero is called the \textbf{balanced} property.
  \end{beamerboxesrounded}
\end{frame}

\begin{frame}{Integral Attack}{Distinguisher}
  \begin{figure}
    \centering
    \includegraphics[width=\linewidth]{sq_attack1}
    \caption{Integral attack distinguisher (Round 1, 2)}
  \end{figure}
\end{frame}

\begin{frame}{Integral Attack}{Distinguisher}
  \begin{figure}
    \centering
    \includegraphics[width=\linewidth]{sq_attack2}
    \caption{Integral attack distinguisher (Round 3, 4)}
  \end{figure}
\end{frame}

\begin{frame}{Integral Attack}{Balanced Property}
  \begin{flalign*}
    \bigoplus_{0 \leq n \leq 255} S_{4,n}^\theta[i,j]
    &= \bigoplus_{0 \leq n \leq 255} \bigoplus_k c_{j-k} S_{4,n}^I[i,k] \label{eq:bal} \\
    &= \bigoplus_l c_l \bigoplus_{0 \leq n \leq 255} S_{4,n}^I[i,l+j] \nonumber \\
    &= \bigoplus_l c_l 0 \nonumber \\ &= 0 \nonumber
  \end{flalign*}
\end{frame}

\begin{frame}{Integral Attack}
  \begin{beamerboxesrounded}{Attack Procedure}
    \begin{itemize}
      \item Guess a byte from $k^4$, say $k^4_{i,j}$.
      \item Use the guess $k^4_{i,j}$ to calculate $S_4^\theta[j,i]$
            \begin{equation*}
              S_4^\theta[j,i] = Sbox^{-1}[S_5^I[i,j] \oplus k_{i,j}^4]
            \end{equation*}
      \item Verify the XOR sum of all 256 values of $S_4^\theta[j,i]$. If it is not balanced then wrong guess.
    \end{itemize}
  \end{beamerboxesrounded}
\end{frame}

\begin{frame}{Integral Attack}
  \begin{beamerboxesrounded}{Sets required}
    \begin{itemize}
      \item Probability that a random XOR sum of 8 bit is zero is $2^{-8}$
      \item With $2^8$ guesses, expected number of subkeys passing is $2^8.2^{-8} = 1$.
      \item Theoretically, 1 $\Lambda$ set is just enough.
      \item For practical purposes, 2 $\Lambda$ sets need to be used for high success probability.
    \end{itemize}
  \end{beamerboxesrounded}

  \vspace{5mm}

  \begin{beamerboxesrounded}{Extended Attacks}
    The 4 round attack can be extended from beginning and end. The $(D,T,M)$ complexities of the 6 round attack are $(2^{32},2^{72},2^{32})$.
  \end{beamerboxesrounded}
\end{frame}

\begin{frame}{Other Attacks}
  \begin{beamerboxesrounded}{Related Key Boomerang Attack}
    \begin{itemize}
      \item Attack on full 8 round cipher
      \item 7 round distinguisher with probability $2^{-119}$
      \item Retrieve 16 bits of key using $2^{123}$ data and $2^{36}$ time
    \end{itemize}
  \end{beamerboxesrounded}
  \vspace{5mm}
  \begin{beamerboxesrounded}{Biclique Cryptanalysis}
    \begin{itemize}
      \item Attack on full 8 round cipher inspired by Biclique Cryptanalysis of AES
      \item $(D,T,M)$ complexities are $(2^{48},2^{126},2^{16})$
    \end{itemize}
  \end{beamerboxesrounded}
\end{frame}

### 2020-11-27 presentation/bpnominate.tex
Add brownie point

@@
 
-\begin{frame}{\#1 Figure showing 4 round distinguisher}
+\begin{frame}{Figure showing 4 round distinguisher}
   \begin{figure}
@@
 
-\begin{frame}{\#2 Integral Attack Implementation}
+\begin{frame}{Observations on DDT}
+  Observations on similarity between AES and SQUARE DDT.
+\end{frame}
+
+\begin{frame}{Integral Attack Implementation}
   C++ Implementation of 4 round integral attack
@@
 
-\begin{frame}{\#3 Similarity of Inverse Cipher}
+\begin{frame}{Similarity of Inverse Cipher}
   The SQUARE cipher and it's inverse are very similar.

### 2020-11-28 presentation/spec.tex
add presentation template
Update spec.tex

--- 2020-11-24 presentation/intro.tex
@@
-\section{Introduction}
+\section{Cipher Specifications}
 
-\begin{frame}{Slide One}
-
+\begin{frame}{SQUARE Cipher}
+  \begin{beamerboxesrounded}{Introduction}
+      Square is an iterated block cipher. Block length and key length is 128 bits.
+      The original design of Square concentrates on the resistance against dierential and linear cryptanalysis.
+However, after integral attack cipher rounds were extended to eight rounds.
+Now,There are total eight rounds in SQUARE cipher.And the round transformation of Square is composed of four distinct transformations($\theta$,$\gamma$,$\pi$,$\sigma$).
+  \end{beamerboxesrounded}
 \end{frame}
 
-\begin{frame}{Slide Two}
-
+\begin{frame}{A Linear Transformation $\theta$}
+    \begin{beamerboxesrounded}{A Linear Transformation ($\theta$)} \\
+        $\theta$ is a linear operation.
+        $$
+        \theta: b=\theta(a) \Leftrightarrow b_{i, j}=c_{j} a_{i, 0} \oplus c_{j-1} a_{i, 1} \oplus c_{j-2} a_{i, 2} \oplus c_{j-3} a_{i, 3}
+        $$
+        Here, $c$ is a 1D array and equivalent to below matrix:-  \\
+        \begin{equation*}
+          c   \equiv \begin{bmatrix}
+            2 & 1 & 1 & 3 \\
+            3 & 2 & 1 & 1 \\
+            1 & 3 & 2 & 1 \\
+            1 & 1 & 3 & 2
+          \end{bmatrix}
+        \end{equation*}
+    \end{beamerboxesrounded}
 \end{frame}
 
-\begin{frame}{Slide Three}
+\begin{frame}{A Nonlinear Transformation $\gamma$}
+    \begin{beamerboxesrounded}{A Nonlinear Transformation ($\gamma$)}\\
+        $\gamma$ is a nonlinear byte substitution, identical for all bytes.
+        $$
+        \gamma: b=\gamma(a) \Leftrightarrow b_{i, j}=\mathrm{S}_{\gamma}\left(a_{i, j}\right)
+        $$
+        Here, $\mathrm{S}$ -box is an invertible 8-bit substitution table. 
+    \end{beamerboxesrounded}
+\end{frame}
 
+\begin{frame}{A Byte Permutation $\pi$}
+    \begin{beamerboxesrounded}{A Byte Permutation ($\pi$)}\\
+        $\pi$ is a linear operation. It transposes a matrix.
+        $$
+        \pi: b=\pi(a) \Leftrightarrow b_{i, j}=a_{j, i}
+        $$
+        $\pi$ is an involution $\iff$ $\pi^{-1}=\pi$
+    \end{beamerboxesrounded}
 \end{frame}
+
+\begin{frame}{Bitwise Round Key Addition $\sigma$}
+    \begin{beamerboxesrounded}{Bitwise Round Key Addition ($\sigma$)}\\
+        $\sigma$ is a linear opeartion.\\
+        $$
+        \sigma\left[k^{t}\right]: b=\sigma\left[k^{t}\right](a) \Leftrightarrow b=a \oplus k^{t}
+        $$
+        $\sigma$ is an involution also hence,
+        the inverse of $\sigma\left[k^{t}\right]$ is $\sigma\left[k^{t}\right]$ itself.
+    \end{beamerboxesrounded}             
+\end{frame}
+
+\begin{frame}{Key scheduling}
+    \begin{beamerboxesrounded}{The Round Key Evolution ($\psi$)}\\
+        The round keys $k^{t}$ are derived from the cipher key $K$. $k^{0}$ equals the cipher key $K$.$\psi$ is a affine transfomation.
+        $$
+        \psi: k^{t}=\psi\left(k^{t-1}\right)
+        $$  
+    \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Rounds}
+    \begin{beamerboxesrounded}{Rounds}
+        There are total eight rounds in SQUARE Cipher proceeded by a key addition $\sigma\left[k^{0}\right]$ and by $\theta^{-1}$ .\\
+        Every round is denoted by $\rho\left[k^{t}\right]$.
+        $$
+        \rho\left[k^{t}\right]=\sigma\left[k^{t}\right] \circ \pi \circ \gamma \circ \theta
+        $$
+
+        In first round $\theta^{-1}$ before $\sigma\left[k^{0}\right]$ are also incorporated:-\\
+        hence,
+        $$
+        \begin{aligned}
+        \rho\left[k^{1}\right] \circ \sigma\left[k^{0}\right] \circ \theta^{-1}\\ &=\sigma\left[k^{1}\right] \circ \pi \circ \gamma \circ \theta \circ \sigma\left[k^{0}\right] \circ \theta^{-1} \\
+        &=\sigma\left[k^{1}\right] \circ \pi \circ \gamma \circ \sigma\left[\theta\left(k^{0}\right)\right]
+        \end{aligned}
+        $$
+    \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Rounds}
+    All eight rounds of SQUARE Cipher:-
+    \begin{beamerboxesrounded}
+        $$
+        \operatorname{SQUARE}[k]=\rho\left[k^{8}\right] \circ \rho\left[k^{7}\right] \circ \rho\left[k^{6}\right] \circ \rho\left[k^{5}\right] \circ \rho\left[k^{4}\right] \circ \rho\left[k^{3}\right] \circ \rho\left[k^{2}\right] \circ \rho\left[k^{1}\right] \circ \sigma\left[k^{0}\right] \circ \theta^{-1}
+        $$
+    \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Properties}
+    \begin{itemize}
+        \item {Inverse Cipher}
+            Square has been designed in such a way that the structure of its inverse is equal to that of the cipher itself, with the exception of the key schedule.
+            $$
+            \begin{array}{l}
+            \text { SQUARE }^{-1}[k]= \\
+            \qquad  \theta \circ \sigma\left[k^{0}\right] \circ \rho^{-1}\left[k^{1}\right] \circ \rho^{-1}\left[k^{2}\right] \circ \rho^{-1}\left[k^{3}\right] \circ              \rho^{-1}\left[k^{4}\right] \circ \rho^{-1}\left[k^{5}\right] \circ \rho^{-1}\left[k^{6}\right] \circ \rho^{-1}\left[k^{7}\right] \circ \rho^{-1}\left[k^{8}\right]
+            \end{array}
+            $$
+            Round transformation  of Inverse cipher as:-
+            $$
+            \rho^{\prime}\left[k^{t}\right]=\sigma\left[k^{t}\right] \circ \pi \circ \gamma^{-1} \circ \theta^{-1}
+            $$
+            Above expression shows the same structure of $\rho{prime}$ as $\rho$ itself, except that $\gamma$ and $\theta$ are replaced by $\gamma^{-1}$ and $\theta^{-1}$    respectively.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Properties}
+\begin{itemize}
+    \item {Confusion\\}
+         Nonlinear Transformation $\gamma$ adds confusion property in the cipher.
+    \item{Diffusion\\}
+         In Square Cipher, transformation operations (Linear Transformation $\theta$, Byte Permutation $\pi$ add diffusion property in the cipher.
+    \item{Security margin\\}
+         Like AES in SQUARE we also have safety rounds.
+Integral attack was known up to six rounds so to make it secure cipher was extended up to eight rounds.
+Now, there are total eight rounds so last two rounds are for security purpose of cipher.
+\end{itemize}
+\end{frame}
+% \end{document}

### 2020-11-28 presentation/intro.tex
fix latex errors

@@
 
-\begin{frame}{Slide One}
-
+\begin{frame}{SQUARE Cipher}
+  \begin{beamerboxesrounded}{Introduction}
+    Square is an iterated block cipher. Block length and key length is 128 bits.
+    The original design of Square concentrates on the resistance against differential and linear cryptanalysis.
+However, after integral attack cipher rounds were extended to eight rounds.
+Now,There are total eight rounds in SQUARE cipher.And the round transformation of Square is composed of four distinct transformations($\theta$,$\gamma$,$\pi$,$\sigma$).
+  \end{beamerboxesrounded}
 \end{frame}
-
-\begin{frame}{Slide Two}
-
-\end{frame}
-
-\begin{frame}{Slide Three}
-
-\end{frame}

### 2020-11-28 presentation/spec.tex
Update spec.tex
fix latex errors

--- 2020-11-24 presentation/intro.tex
@@
-\section{Introduction}
+\section{Cipher Specifications}
 
-\begin{frame}{Slide One}
+\begin{frame}{A Linear Transformation $\theta$}
+  \begin{beamerboxesrounded}{A Linear Transformation ($\theta$)}
+    $\theta$ is a linear operation.
+    $$
+      \theta: b=\theta(a) \Leftrightarrow b_{i, j}=c_{j} a_{i, 0} \oplus c_{j-1} a_{i, 1} \oplus c_{j-2} a_{i, 2} \oplus c_{j-3} a_{i, 3}
+    $$
+    Here, $c$ is a 1D array and equivalent to below matrix:
 
+    \begin{equation*}
+      c   \equiv \begin{bmatrix}
+        2 & 1 & 1 & 3 \\
+        3 & 2 & 1 & 1 \\
+        1 & 3 & 2 & 1 \\
+        1 & 1 & 3 & 2
+      \end{bmatrix}
+    \end{equation*}
+  \end{beamerboxesrounded}
 \end{frame}
 
-\begin{frame}{Slide Two}
-
+\begin{frame}{A Nonlinear Transformation $\gamma$}
+  \begin{beamerboxesrounded}{A Nonlinear Transformation ($\gamma$)}
+    $\gamma$ is a nonlinear byte substitution, identical for all bytes.
+    $$
+      \gamma: b=\gamma(a) \Leftrightarrow b_{i, j}=\mathrm{S}_{\gamma}\left(a_{i, j}\right)
+    $$
+    Here, $\mathrm{S}$ -box is an invertible 8-bit substitution table.
+  \end{beamerboxesrounded}
 \end{frame}
 
-\begin{frame}{Slide Three}
+\begin{frame}{A Byte Permutation $\pi$}
+  \begin{beamerboxesrounded}{A Byte Permutation ($\pi$)}
+    $\pi$ is a linear operation. It transposes a matrix.
+    $$
+      \pi: b=\pi(a) \Leftrightarrow b_{i, j}=a_{j, i}
+    $$
+    $\pi$ is an involution $\iff$ $\pi^{-1}=\pi$
+  \end{beamerboxesrounded}
+\end{frame}
 
+\begin{frame}{Bitwise Round Key Addition $\sigma$}
+  \begin{beamerboxesrounded}{Bitwise Round Key Addition ($\sigma$)}
+    $\sigma$ is a linear opeartion.
+
+    $$
+      \sigma\left[k^{t}\right]: b=\sigma\left[k^{t}\right](a) \Leftrightarrow b=a \oplus k^{t}
+    $$
+    $\sigma$ is an involution also hence,
+    the inverse of $\sigma\left[k^{t}\right]$ is $\sigma\left[k^{t}\right]$ itself.
+  \end{beamerboxesrounded}
 \end{frame}
+
+\begin{frame}{Key scheduling}
+  \begin{beamerboxesrounded}{The Round Key Evolution ($\psi$)}
+    The round keys $k^{t}$ are derived from the cipher key $K$. $k^{0}$ equals the cipher key $K$.$\psi$ is a affine transfomation.
+    $$
+      \psi: k^{t}=\psi\left(k^{t-1}\right)
+    $$
+  \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Rounds}
+  \begin{beamerboxesrounded}{Rounds}
+    There are total eight rounds in SQUARE Cipher proceeded by a key addition $\sigma\left[k^{0}\right]$ and by $\theta^{-1}$.
+
+    Every round is denoted by $\rho\left[k^{t}\right]$.
+    $$
+      \rho\left[k^{t}\right]=\sigma\left[k^{t}\right] \circ \pi \circ \gamma \circ \theta
+    $$
+
+    In first round $\theta^{-1}$ before $\sigma\left[k^{0}\right]$ are also incorporated:-\\
+    hence,
+    $$
+      \begin{aligned}
+        \rho\left[k^{1}\right] \circ \sigma\left[k^{0}\right] \circ \theta^{-1}                               \\ &=\sigma\left[k^{1}\right] \circ \pi \circ \gamma \circ \theta \circ \sigma\left[k^{0}\right] \circ \theta^{-1} \\
+         & =\sigma\left[k^{1}\right] \circ \pi \circ \gamma \circ \sigma\left[\theta\left(k^{0}\right)\right]
+      \end{aligned}
+    $$
+  \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Rounds}
+  All eight rounds of SQUARE Cipher:
+
+  \begin{beamerboxesrounded}{SQUARE}
+    \begin{flalign*}
+      SQUARE[k]&=\rho\left[k^{8}\right] \circ \rho\left[k^{7}\right] \circ \rho\left[k^{6}\right] \circ \rho\left[k^{5}\right] \circ \rho\left[k^{4}\right] \circ \rho\left[k^{3}\right] \circ \\& \rho\left[k^{2}\right] \circ \rho\left[k^{1}\right] \circ \sigma\left[k^{0}\right] \circ \theta^{-1}
+    \end{flalign*}
+  \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{SQUARE Cipher}
+  \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{Square_cipher_diagram}
+    \caption{SQUARE cipher encryption}
+  \end{figure}
+\end{frame}
+\begin{frame}{Properties}
+  \begin{itemize}
+    \item {Inverse Cipher}
+          Square has been designed in such a way that the structure of its inverse is equal to that of the cipher itself, with the exception of the key schedule.
+          \begin{flalign*}
+            \text { SQUARE }^{-1}[k]&=
+            \qquad  \theta \circ \sigma\left[k^{0}\right] \circ \rho^{-1}\left[k^{1}\right] \circ \rho^{-1}\left[k^{2}\right] \\&  \circ \rho^{-1}\left[k^{3}\right] \circ              \rho^{-1}\left[k^{4}\right] \circ \rho^{-1}\left[k^{5}\right] \circ \rho^{-1}\left[k^{6}\right] \\&  \circ \rho^{-1}\left[k^{7}\right] \circ \rho^{-1}\left[k^{8}\right]
+          \end{flalign*}
+
+          Round transformation  of Inverse cipher as:-
+          $$
+            \rho^{\prime}\left[k^{t}\right]=\sigma\left[k^{t}\right] \circ \pi \circ \gamma^{-1} \circ \theta^{-1}
+          $$
+          Above expression shows the same structure of $\rho{prime}$ as $\rho$ itself, except that $\gamma$ and $\theta$ are replaced by $\gamma^{-1}$ and $\theta^{-1}$    respectively.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Properties}
+  \begin{itemize}
+    \item {Confusion\\}
+          Nonlinear Transformation $\gamma$ adds confusion property in the cipher.
+    \item{Diffusion\\}
+          In Square Cipher, transformation operations (Linear Transformation $\theta$, Byte Permutation $\pi$ add diffusion property in the cipher.
+    \item{Security margin\\}
+          Like AES in SQUARE we also have safety rounds.
+Integral attack was known up to six rounds so to make it secure cipher was extended up to eight rounds.
+Now, there are total eight rounds so last two rounds are for security purpose of cipher.
+  \end{itemize}
+\end{frame}
+% \end{document}
